Object-Oriented Internet - Azure Interoperability

### 2020-11-29 Latex/Manuscript.tex
Prepare Abstract #30
- fixes #30

\begin{abstract}
      TBD
\end{abstract}

@@

Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology. It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e. Industry 4.0 (I4.0) and the Internet of Things (IoT) (Sect. \ref*{introduction}).

>>>>

\begin{abstract}

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. To deal with the network traffic propagation asymmetry or assets mobility the reactive interoperability relationship of the interconnected nodes is proposed. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements. To promote separation of concerns and reusability, the implementation of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.

      The proposals are backed by proof of concept reference implementations conforming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario. It is in contrast to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.

\end{abstract}

@@

Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology. It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e. Industry 4.0 and the Internet of Things (Sect. \ref*{introduction}).
